Uncovering underlying high-level musical content in the temporal domain \\ \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks

### 2023-05-10 figures/neural networks/manifold.tex
Updates from Overleaf

    \caption[High-level diagram of dimensionality reduction and latent space representation.]{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}
    \label{fig:my_label}
\end{figure}

>>>>

    \caption[High-level diagram of dimensionality reduction and latent space representation.]{\small{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}}
    \label{fig:my_label}
\end{figure}

### 2023-05-10 figures/neural networks/pipeline.tex
Updates from Overleaf

\begin{tikzpicture}[
    line cap=round, thick,
    stage/.style={shape=circle, draw, font=\bfseries, minimum width=2*\circRad},
    challenge/.style={draw, very thin, inner sep=2, rounded corners=2},
    every node/.style={align=center},
  ]
\centering
\scalebox{0.7}{
  \begin{scope}[local bounding box=challenges]
    % Data
    \node [stage, fill=orange!40] (data) {Data\\Challenges};
    \foreach \itm [count=\i, evaluate={\a=\i*15+120;}] in
      {volume, velocity, variety, veracity, visualization, long-term storage, standardization} {
        \node[challenge] at (\a:\circRad + 2mm) [rotate=\a+180, anchor=east] {\itm};
        \draw (\a:\circRad + 2mm) -- (\a:\circRad);
      }

    % Descriptor
    \begin{scope}[xshift=6cm]
      \node [stage, fill=yellow!40] (descriptor) {Descriptor\\Challenges};
      \foreach \itm [count=\i, evaluate={\a=\i*15+140;}] in
        {symmetry invariance, translation, rotation, permutation} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a+180, anchor=east] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
      \foreach \itm [count=\i, evaluate={\a=30-\i*15;}] in
        {efficiency, speed, compactness} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a, anchor=west] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
    \end{scope}

    % Model
    \begin{scope}[xshift=12cm]
      \node [stage, fill=blue!20] (model) {Model\\Challenges};
      \foreach \itm [count=\i, evaluate={\a=70-\i*16;}] in
        {reproducibility, benchmarking, transfer learning, extrapolation, {sharing model+results}, computational cost, incorporate physics} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a, anchor=west] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
    \end{scope}
  \end{scope}

  \draw[ultra thick,->] (data.-70) to [bend right] (descriptor.-110);
  \draw[ultra thick,->] (descriptor.70) to [bend left] (model.110);
    }
\end{tikzpicture}

>>>>

\begin{figure}
    \centering
    \begin{tikzpicture}[
    line cap=round, thick,
    stage/.style={shape=circle, draw, font=\bfseries, minimum width=2*\circRad},
    challenge/.style={draw, very thin, inner sep=2, rounded corners=2},
    every node/.style={align=center},
  ]
\centering
\scalebox{0.7}{
  \begin{scope}[local bounding box=challenges]
    % Data
    \node [stage, fill=orange!40] (data) {Data\\Challenges};
    \foreach \itm [count=\i, evaluate={\a=\i*15+120;}] in
      {volume, variety, integrity, accessibility, reproduciability} {
        \node[challenge] at (\a:\circRad + 2mm) [rotate=\a+180, anchor=east] {\itm};
        \draw (\a:\circRad + 2mm) -- (\a:\circRad);
      }

    % Transformations
    \begin{scope}[xshift=6cm]
      \node [stage, fill=yellow!40] (descriptor) {Augmentation\\Challenges};
      \foreach \itm [count=\i, evaluate={\a=\i*15+140;}] in
        {meaningful, useful, not harmful,} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a+180, anchor=east] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
      \foreach \itm [count=\i, evaluate={\a=30-\i*15;}] in
        {efficiency, speed, compactness, computational cost} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a, anchor=west] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
    \end{scope}

    % Model
    \begin{scope}[xshift=12cm]
      \node [stage, fill=blue!20] (model) {Model\\Challenges};
      \foreach \itm [count=\i, evaluate={\a=70-\i*16;}] in
        {transfer learning, computational cost, performance, evaluation} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a, anchor=west] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
    \end{scope}
  \end{scope}

  \draw[ultra thick,->] (data.-70) to [bend right] (descriptor.-110);
  \draw[ultra thick,->] (descriptor.70) to [bend left] (model.110);
    }
\end{tikzpicture}
    \caption[Challenges in Data, Augmentation, and Model Stages]{\small{A visual representation of the challenges in three main stages of a machine learning pipeline: Data, Augmentation, and Model. The Data stage includes challenges such as volume, variety, integrity, accessibility, and reproducibility. The Augmentation stage covers challenges related to creating meaningful, useful, and not harmful augmentations while considering efficiency, speed, compactness, and computational cost. The Model stage addresses challenges in transfer learning, computational cost, performance, and evaluation. Arrows indicate the flow of progression from one stage to another.}}

    \label{fig:my_label}
\end{figure}

### 2023-05-10 introduction/Subsections/Assumptions.tex
Updates from Overleaf

>>>>

\begin{figure}
    \centering
    \scalebox{0.9}{
    \includegraphics[width=\textwidth]{figures/images/Mahler 9 Giant Steps score.png}
        }
    \caption[Mahler's 9th Symphony, 2nd movement]{\small{A small excerpt from Mahler's 9th Symphony, 2nd movement: The melodic and harmonic contour propels through non-diatonic major thirds.}}
    \label{fig:mahler}
\end{figure}

\begin{figure}
    \centering
    \scalebox{0.9}{
    \includegraphics[width=\textwidth]{figures/images/giant steps score.png}
        }
    \caption[Giant Steps]{\small{John Coltrane's Giant Steps head: A testament to harmonic exploration, featuring rapid chord changes in non-diatonic major thirds.}}
    \label{fig:giant_steps}
\end{figure}

\begin{figure}
    \centering
    \scalebox{0.9}{
    \includegraphics[width=\textwidth]{figures/images/train interlude score.png}
        }
    \caption[Last Train Home]{\small{Pat Metheny's Last Train Home interlude.}}
    \label{fig:last_train}
\end{figure}
